### 2023-03-16 paper.tex
Add some corrections

\begin{abstract}
  This paper discusses three language models based on the transformer architecture.
  I aim decipher some differences between the models which seem very similar at first glance.
  The paper also takes a look at some applications and extensions to basic language
  models and some problems present in large language models, including biases
  and hallucination.
\end{abstract}

@@

The three different models are all similar in architecture being mostly
faithful to the original transformer architecture as presented in 
\cite{vaswani_attention_2017}. However, each of them have a different approach
to using the decoder and encoder stacks of the transformer. GPT uses only
the decoder, BERT only the encoder and T5 both encoder and decoder
\cite{radford_improving_nodate,devlin_bert_2019,raffel_exploring_2020}.

\section{Training}
All three of the models this paper discusses use transfer learning for 
training. The general idea is to first train a baseline model unsupervised 
using a large amount of unstructured text and then fine tuning the model
for each specific task after.

The objective of the unsupervised pre-training stage is to teach the model
general language understanding. The exact details between models varies but
in general, a massive number tokens are fed into to model during the course
of training. Each word corresponds to a single or a few tokens depending on 
the encoding used [citation needed, same as pricing] and the number of tokens
used in training can go up to the trillions \cite{raffel_exploring_2020}. 
The model is asked to predict a missing token based on context.

>>>>

\begin{abstract}
  This paper discusses three language models based on the transformer architecture.
  I aim to decipher some differences between the models which seem very similar at first glance.
  The paper also takes a look at some applications and extensions to basic language
  models and some problems present in large language models, including biases
  and hallucination.
\end{abstract}

@@

The three different models are all similar in architecture being mostly
faithful to the original transformer architecture as presented in 
\cite{vaswani_attention_2017}. However, each of them have a different approach
to using the decoder and encoder stacks of the transformer. GPT uses only
the decoder, BERT only the encoder and T5 both the encoder and decoder
\cite{radford_improving_nodate,devlin_bert_2019,raffel_exploring_2020}.

\section{Training}
All three of the models this paper discusses use similar approaches for 
training. The general idea is to first train a baseline model unsupervised 
using a large amount of unstructured text and then fine tuning the model
for each specific task after.

The objective of the unsupervised pre-training stage is to teach the model
general language understanding. The exact details between models varies but
in general, a massive number tokens are fed into to model during the course
of pre-training. Each word corresponds to a single or a few tokens depending on 
the encoding used [citation needed, same as pricing] and the number of tokens
used in training can go up to the trillions \cite{raffel_exploring_2020}. 
The model is asked to predict a missing token based on context.
